### 2021-05-26 article/article.tex
update

\subsection{Probability effects in the GeV range}
In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
(e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
the three different effects in Fig.~\ref{fig:nsi_probs}.

Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
\begin{figure}
   \includegraphics[width=0.95\textwidth]{figures/nsi_probs.pdf}
   \caption{The three different effects that the off-diagonal NSI parameters have in the \si{\GeV} range.}\label{fig:nsi_probs}
\end{figure}

\section{Detector formalism}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption.
%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?

The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we plot the flux in region in which 99\% of the 
DeepCore track events originating from $\nm$ fluxes are contained. In the right panel, we show the same but with IceCube events. We see that the only clear signal discernible to the IceCube detector
is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
is exposed to multiple fringes of flux surpluses with a factor in the order of $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensitive IceCube deficiency.
%TODO: check values above after final plot of flux ratios

@@

\subsection{IceCube}\label{ch:ICmethod}
We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which was collected over 8 years. The event rate for each bin reads
\begin{align}\label{eq:ICevents}
   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}(E^t,\theta^t)  A^\text{eff}(E^t) R(E^r,E^t) 
   \dd E^t\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased, which means that we don't assume that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.

@@

% We plot the normalized event difference $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
% assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This illustrates the expected sensitivity of DeepCore for the NSI parameters.
%TODO:conclusion from this?

@@

\section{Results}
In this section, we present the results from the experiments alone, as well as jointly. 
\subsection{Methodology}\label{sec:method}
%TODO a sentence about simplicity
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. 
We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

@@

\subsection{Constraining the NSI parameters}
First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
confidence levels in Table~\ref{table:IC_DC_results} and Table~\ref{table:PINGU_joint_results}, and best-fit points in Table~\ref{table:bestfit}.

@@

We see asymmetrical shapes in the $\Delta \chi^2$ plots in Fig.~\ref{fig:3D_NO}, especially in $\emt$ and $\eet$.%TODO: make better
We investigate this for $\emt$ by plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
%TODO: check that this is what is plotted.
$\epsilon^\pm_{\mu\tau} = \pm 0.01$ in Fig.~\ref{fig:Pmm_asymmetry}.
Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ to explain the $\emt$ asymmetry. 
Let $P^\pm$ denote $P_{\mu\mu}(\epsilon^\pm_{\mu\tau})$. 
We see see that $\emt^+$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
while $\emt^-$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
is indeed preserved at flux level. So the flux for $\emt^+$ is higher than the flux for $\emt^-$. Is this still true at event level, i.e. after reconstruction? 
As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt^-$. DeepCore on the other hand, 
has fewer bins where the event count for $\emt^-$ surpasses the event count for $\emt^+$, giving weaker statistics for the negative side. Thus, we conclude that the DeepCore
$\emt$ asymmetry stems from the lower statistics for negative $\emt$ at probability level, which is then propagated through the flux and finally affects the reconstruction. %TODO: fill more conclusion?

Comparing Fig.~\ref{fig:emt_events} with the flux ratios in Fig.~\ref{fig:flux_ratio}, we see that the reconstruction of PINGU is
superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})}$ (which is in reconstructed quantities) more closely matches the flux ratio $\log{(\phi_{NSI}/\phi_{SI})}$ (which is in true quantities).
This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes while PINGU still has the $N^-_{NSI}$ surplus below \SI{10}{\GeV}.

@@

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
\begin{align}\label{eq:joint_chisq}
    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
\end{align}
with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
The results are shown in Fig.~\ref{fig:IC_NO} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
\newpage

>>>>

To propagate the neutrino states through the Earth, we solve the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. 
The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption. After this, we are
ready to study the NSI effect on probability level.
%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?

\subsection{Non-standard effects in the GeV-TeV range}\label{sec:nsiEffects}
Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.

In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
(e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
the three different effects in Fig.~\ref{fig:nsi_probs}.

Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
\begin{figure}
   \includegraphics[width=0.95\textwidth]{figures/nsi_probs.pdf}
   \caption{The three different effects that the off-diagonal NSI parameters have in 
   the \si{\GeV} range. To schematically elucidate the NSI effect, we plot the summed probabilities for both neutrinos and 
   antineutrinos.}\label{fig:nsi_probs}
\end{figure}%TODO: change plot ylabels

To study the NSI flux effect, we propagate the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth.
The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ at flux level, 
we plot in Fig.~\ref{fig:flux_ratio} the quantity $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$, 
where all fluxes are propagated to detector level by Eq.~\ref{eq:propFlux}. 
In the left panel, we plot the flux in region in which 99\% of the 
DeepCore track events originating from $\nm + \anm$ fluxes are contained. In the right panel, we show the same but with IceCube events. We see that the only clear signal discernible to the IceCube detector
is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
is exposed to multiple fringes of flux surpluses with a factor in the order of $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensitive IceCube deficiency.
%TODO: check values above after final plot of flux ratios

@@

\section{Detector formalism}
\subsection{IceCube}\label{ch:ICmethod}
We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which was collected over 8 years. The event rate for each bin reads
\begin{align}\label{eq:ICevents}
   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}(E^t,\theta^t)  A^\text{eff}(E^t) R(E^r,E^t) 
   \dd E^t\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased, which means that we don't assume that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.

@@

@@

\section{Results}
At the reconstructed event level, we note that the $\emt$ features discussed in Sec.~\ref{sec:nsiEffects} display themselves differently in each detector.
We investigate this for $\emt$ by in Fig.~\ref{fig:Pmm_asymmetry} plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
%TODO: check that this is what is plotted.
$\epsilon^\pm_{\mu\tau} = \pm 0.01$.
Comparing Fig.~\ref{fig:Pmm_asymmetry} with the flux ratios in Fig.~\ref{fig:emt_events}, we see that the reconstruction of PINGU is
superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})} = \log{N^+_{NSI}} - \log{N^-_{NSI}}$ (in reconstructed quantities) 
more closely matches the probability difference $P^+-P^-$ (in true quantities).
This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes while PINGU preserves the $N^-_{NSI}$ surplus below \SI{10}{\GeV}.

Now we turn to the effect of $\emt$. Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ in this way to explain the $\emt$ features. 
First, let $P^\pm$ denote $P_{\mu\mu}(\epsilon^\pm_{\mu\tau})$. 
We see see that $\emt^+$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
while $\emt^-$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
is indeed preserved at flux level. So the flux for $\emt^+$ is higher than the flux for $\emt^-$. Is this still true at event level, i.e. after reconstruction? 
As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, which will give a high statistics on both sides of $\emt=0$, slightly favoring $\emt^-$. 
DeepCore on the other hand, has fewer bins where the event count for $\emt^-$ surpasses the event count for $\emt^+$, 
giving weaker statistics for the negative side. Thus, we conclude that we will see a $\emt$ \si{GeV}-asymmetry stemming from the lower statistics 
for negative $\emt$ at probability level, which is then propagated through the flux and finally affects the reconstruction. %TODO: fill more conclusion?

\subsection{Constraining the NSI parameters}\label{sec:method}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. 
We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

@@

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
\begin{align}\label{eq:joint_chisq}
    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
\end{align}
with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.

Now, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. The results are shown in Fig.~\ref{fig:IC_NO} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.

Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.

@@

@@

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
\newpage
